### 2022-02-14 documentos/kraus.tex
I just evaluated random code in my console
avanzando a Kraus y typos en mi apendice

\cpnote{Crep qe hay que hacer una mini introduccion en donde se explique el porqué de
esta seccion. Básicamente la idea es conectar estos bichos con procesos fisicos.
Siento que la introduccion propuesta est´a un poco debil}

@@

{\red [anterior]Given that \pce{} channels are projections, we might ask whether they are fixed
points of some memory-less (Markovian) process or not. In this section we prove
that they are, and give two examples of Markovian implementations. The first
one consist in identifying each \pce{} channel as a fixed point of some pure
dissipative process. The second, in identifying each \pce{} channel as fixed
points of some memory-less collision model.}
{\blue [nuevo, sigo trabajando] It is known that not every quantum channel can be seen as a snapshot of a Markovian decoherence process~\cite{cirac,davalosdivisibility}, \ie{} a process described with a Markovian master equation,
\begin{multline}
\dot \rho(t)=-i [H(t),\rho(t)]+\\
\sum_k \gamma_k(t)\left( V_k(t)\rho(t)V_k^{\dagger{}}-\frac{1}{2} \left\{V_k^\dagger{} V_k(t),\rho(t) \right\}\right)
\end{multline}
 \pce{} channels erase information
The first
one consist in identifying each \pce{} channel as a fixed point of some pure
dissipative process. The second, in identifying each \pce{} channel as fixed
points of some memory-less collision model.
}
% }}}
\subsection{Kraus representation} % {{{
To derive the aforementioned implementations, we exploit the existence of the
PCEGs and their \textit{Kraus representation} (or operator-sum representation)
which, for an arbitrary channel $\mcE$,  reads 
\begin{equation}
\mcE[\rho]=\sum_i K_i \rho
K_i^\dagger{},
\end{equation}
with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
% The Kraus operators corresponding to one single qubit PCEs are 
% $\{\openone/\sqrt2, \sigma_i/\sqrt2\}$,
% % \begin{equation}
% % \{\openone/\sqrt2, \sigma_i/\sqrt2\}
% % \label{eq:kraus:PCE}
% % \end{equation}
% corresponding to the operation that leaves the component $\sigma_i$
% invariant~\cite{nielsen_chuang_2011}.
Inspection of the Kraus operators of two qubit PCEG leads to
the ansatz that the Kraus operators for the generator of 
$\mcG_{\vec \alpha}$ are 
\begin{equation}
K_0=\frac{\openone}{\sqrt2}, \quad K_1=\frac{\sigma_{\vec \alpha}}{\sqrt2},
% \left\{\openone/\sqrt2, 
% \left(\bigotimes_{k=1}^N \sigma_{\alpha_k}\right)/\sqrt2\right\}. 
\label{eq:kraus:PCE}
\end{equation}
since the Kraus operators corresponding to one single qubit PCEs are 
$\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
corresponding to the operation that leaves the component $\sigma_\alpha$
invariant~\cite{nielsen_chuang_2011}.

>>>>

\cpnote{Crep qe hay que hacer una mini introduccion en donde se explique el porqué de
esta seccion. Básicamente la idea es conectar estos bichos con procesos fisicos.
Siento que la introduccion propuesta est´a un poco debil}
\ddnote{hecha miniintroduccion, es basicamente la misma idea, pero con detalles y justificaciones matematicas}

@@

{\red [anterior]Given that \pce{} channels are projections, we might ask whether they are fixed
points of some memory-less (Markovian) process or not. In this section we prove
that they are, and give two examples of Markovian implementations. The first
one consist in identifying each \pce{} channel as a fixed point of some pure
dissipative process. The second, in identifying each \pce{} channel as fixed
points of some memory-less collision model.}
{\blue [nuevo, sigo trabajando] It is known that not every quantum channel can be seen as a snapshot of a Markovian decoherence process~\cite{cirac,davalosdivisibility}, \ie{} a process described with a Markovian master equation~\cite{lindblad,kossa,kossa2,Gorini1976},
\begin{multline}
\dot \rho(t)=-i [H(t),\rho(t)]+\\
\sum_k \gamma_k(t)\left( V_k(t)\rho(t)V_k^{\dagger{}}-\frac{1}{2} \left\{V_k^\dagger{} V_k(t),\rho(t) \right\}\right),
\end{multline}
where the first part is the so-called Hamiltonian term, the second the dissipative term with $\gamma_k(t)\geq 0$ the relaxation ratios associated with the Lindblad operators $V_k(t)$.
%
In the particular case where the Hamiltonian, relaxation rations and Lindblad operators are independent of time, we recover the well-known Lindblad master equations~\cite{lindblad}. Such equations model time-homogeneous processes, implying one-parameter semigroup structures that will be exploited later.
%
Besides, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$. Furthermore, channels belonging to one-parameter semigroup families usually have non-negative eigenvalues~\cite{davalosdivisibility}
%
Thus we might ask whether 
 \pce{} channels erase information
The first
one consist in identifying each \pce{} channel as a fixed point of some pure
dissipative process. The second, in identifying each \pce{} channel as fixed
points of some memory-less collision model.
}
% }}}
\subsection{Kraus representation} % {{{
To derive the aforementioned implementations, we exploit the existence of the
PCEGs and their \textit{Kraus representation} (or operator-sum representation)
which, for an arbitrary channel $\mcE$,  reads 
\begin{equation}
\mcE[\rho]=\sum_i K_i \rho
K_i^\dagger{},
\end{equation}
with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
% The Kraus operators corresponding to one single qubit PCEs are 
% $\{\openone/\sqrt2, \sigma_i/\sqrt2\}$,
% % \begin{equation}
% % \{\openone/\sqrt2, \sigma_i/\sqrt2\}
% % \label{eq:kraus:PCE}
% % \end{equation}
% corresponding to the operation that leaves the component $\sigma_i$
% invariant~\cite{nielsen_chuang_2011}.
Inspection of the Kraus operators of two qubit PCEG leads to
the ansatz that the Kraus operators for the generator of 
$\mcG_{\vec \alpha}$ are 
\begin{equation}
K_0=\frac{\openone}{\sqrt2}, \quad K_1=\frac{\sigma_{\vec \alpha}}{\sqrt2},
% \left\{\openone/\sqrt2, 
% \left(\bigotimes_{k=1}^N \sigma_{\alpha_k}\right)/\sqrt2\right\}. 
\label{eq:kraus:PCE}
\end{equation}
since the Kraus operators corresponding to one single qubit PCEs are 
$\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
corresponding to the operation that leaves the component $\sigma_\alpha$
invariant~\cite{nielsen_chuang_2011}.

### 2022-02-14 documentos/quantum_classical.tex
avanzando a Kraus y typos en mi apendice

\section{Quantum-Classical channels}
\label{quantum_classical}
\ddnote{Alguien revise este apendice, tiene solo una iterada}
A Quantum-classical (QC) channel is defined using an orthonormal basis in the Hilbert space. Let $B=\left\{ \ket{\psi_i} \right\}$ such a basis in $\hilbert$ with $\dim(\hilbert)=2^N$, the QC associated to $B$ is
\begin{equation}
\mcE^{\text{QC}}_B[\rho]=\sum_{i=1}^{2^N} \bra{\psi_i}\rho \ket{\psi_i} \projj{\psi_i},
\end{equation}
this is, QC channels project density matrices onto the corresponding diagonal matrix in the basis $B$~\cite{nathanson2007pauli}.

Consider now that the basis $B$ is the simultaneous eigenbasis of a maximal set of commuting Pauli strings denoted by $\text{set}(B)$, such set contains $2^N$ elements (including the identity), and there are $2^N+1$ of such sets~\cite{Lawrence2002}. We will prove that the QCs defined in this way are \pce{} channels with $2^N$ on their diagonal.

>>>>

\section{Quantum-Classical channels}
\label{quantum_classical}
\ddnote{Alguien revise este apendice, tiene solo una iterada}
A Quantum-classical (QC) channel is defined using an orthonormal basis in the Hilbert space. Let $B=\left\{ \ket{\psi_i} \right\}$ such a basis in $\hilbert$ with $\dim(\hilbert)=2^N$, the QC channel associated to $B$ is
\begin{equation}
\mcE^{\text{QC}}_B[\rho]=\sum_{i=1}^{2^N} \bra{\psi_i}\rho \ket{\psi_i} \projj{\psi_i},
\end{equation}
this is, QC channels project density matrices onto the corresponding diagonal matrix in the basis $B$~\cite{nathanson2007pauli}.

Consider now that the basis $B$ is the simultaneous eigenbasis of a maximal set of commuting Pauli strings denoted by $\text{set}(B)$, such set contains $2^N$ elements (including the identity), and there are $2^N+1$ of such sets~\cite{Lawrence2002}. We will prove that the QCs defined in this way are \pce{} channels with $2^N$ $1$s on their diagonal.
